Cluster Paper

### 2015-05-04 ms.tex
added full knowledge figure
started work on hetdex selection

\subsection{Dynamical Mass}
Recently, the relationship between the velocity dispersion and dynamical mass has been the focus of several studies (\eg, \citealt{Evrard2008, Saro2013, Sifon2013, VanderBurg2014}), and find a best-fitting relation for the mass enclosed by $r_{200c}$ of the form
\begin{equation}
	M_{200c} = \frac{10^{15}}{h(z)} \bigg{(}\frac{\sigma_{1D}}{\sigma_{15}} \bigg{)}^{-\alpha} \Msol
\end{equation}
where $\sigma_{15} = 1082.9 \pm 4.0 \kms$, $\alpha = 0.3361 \pm 0.0026$, $h(z) = H_0 \sqrt{\Omega_\Lambda + (1+z)^3\Omega_M}$, and $\sigma_{1D}$ is the 1D velocity dispersion of the dark matter particles, which is related to the velocity dispersions of the galaxies.

@@

\subsection{Full Knowledge}
We compare the calculated cluster redshifts to the true redshift ($z_{c,true}$) for 107748 galaxies comprising 1683 unique halos, and we find a RMS$[\Delta z/(1+z_{c,true})]= 4\times 10^{-4}$ where $\Delta z = z_{c,true} - z_{c}$. \editorial{The RMS using just the regular mean is 3.8e-4 which is only slightly better than the biweight. I don't think that will be the case when we get more complicated things.}

\subsection{\ion{O}{ii} Luminosity}

@@

\begin{figure} 
	\includegraphics[width=0.49\textwidth]{oii_sdss.pdf} 
	\caption{} \label{fig:oii sdss} 
\end{figure}

@@

\section{IMPROVEMENT}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
\section{SUMMARY}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
\bibliography{master}

>>>>

\subsection{Dynamical Mass}
Recently, the relationship between the velocity dispersion and dynamical mass has been the focus of several studies (\eg, \citealt{Evrard2008, Saro2013, Sifon2013, VanderBurg2014}), and find a best-fitting relation for the mass enclosed by $r_{200c}$ of the form
\begin{equation}
	M_{200c} = \frac{10^{15}}{h(z)} \bigg{(}\frac{\sigma_{1D}}{\sigma_{15}} \bigg{)}^{-\alpha} \Msol
\end{equation}
where $\sigma_{15} = 1082.9 \pm 4.0~\kms$, $\alpha = 0.3361 \pm 0.0026$, $h(z) = H_0 \sqrt{\Omega_\Lambda + (1+z)^3 \Omega_M}$, and $\sigma_{1D}$ is the 1D velocity dispersion of the dark matter particles, which is related to the velocity dispersions of the galaxies. \editorial{This doesn't appear to be the formula that I am actually using to calculate the mass. I think I am using the relation from Saro2013.}

@@

\subsection{Full Knowledge}
We compare the calculated cluster redshifts to the true redshift ($z_{c,true}$) for 114903 galaxies comprising 1379 unique halos, and we find a RMS$[\Delta z/(1+z_{c,true})]= 4\times 10^{-4}$ where $\Delta z = z_{c,true} - z_{c}$. \editorial{The RMS using just the regular mean is 3.8e-4 which is only slightly better than the biweight. I don't think that will be the case when we get more complicated things.}

\begin{figure*} 
	\includegraphics[width=\textwidth]{fullKnowledge.pdf} 
	\caption{Intrinsic cluster properties versus the recovered cluster properties for 1379 unique halos comprised of 114903 individual galaxies. The left panel shows the line of sight velocity dispersion (LOSVD) and the right panel shows the recovered halo mass. In both panels, the red line shows the 1:1 relation and the teal line shows the best fit to data.} 
	\label{fig:full} 
\end{figure*}

\subsection{HETDEX Depth}

\subsubsection{\ion{O}{ii} Luminosity}

@@

\begin{figure} 
	\includegraphics[width=0.49\textwidth]{oii_sdss.pdf} 
	\caption{686184 $z<0.2$ galaxies} \label{fig:oii sdss} 
\end{figure}

@@

\begin{eqnarray}
	g_{DES} = g_{SDSS} - 0.104*(g-r)_{SDSS} + 0.01 \\
	r_{DES} = r_{SDSS} - 0.102*(g-r)_{SDSS} + 0.02
\end{eqnarray}

\section{IMPROVEMENT}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\section{SUMMARY}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
\bibliography{master}
